---
title: "Analysis"
author: "Brianna Penkala, Kai Hoeger"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
header-includes:
    - \usepackage{caption}
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stargazer)
library(scales)
library(corrplot)
library(extrafont)
library(huxtable)
library(ivreg)
library(sf)
library(patchwork)
library(broom)
library(sandwich)
```

\captionsetup[table]{labelformat=empty}

## Data structuring 

```{r, echo = FALSE}
# Aid data setup

aid_data <- read.csv("/Users/briannapenkala/Downloads/Capstone/Aid CSV.csv")

# Fixing things
aid_data <- aid_data[,c(3,4,5,7,10,13,20,23,51)]
aid_data$tot_activity_value_constant_currency <- gsub(",", "", aid_data$tot_activity_value_constant_currency) #euros
aid_data <- aid_data %>%
  mutate(tot_activity_value_constant_currency = as.numeric(tot_activity_value_constant_currency)) %>%
  mutate(announcement_date = as.Date(announcement_date, format = "%m/%d/%y")) %>%
  rename(date = announcement_date)
aid_data$antidrone_aid[is.na(aid_data$antidrone_aid)] <- 0

# Fixing Finland typo ****************** (check for consistency in case rows change)
aid_data <- aid_data %>%
  mutate(donor = ifelse(donor == "FInland", "Finland", donor))

# Military aid only, adding month row for testing
aid_data <- aid_data %>%
  filter(aid_type_general == "Military", 
         short_term == 1) %>%
  mutate(month = format(date, "%Y-%m"))

# # Patriot missile defense system dataset
# missile_aid_df <- aid_data %>%
#   filter(Patriot.aid == TRUE) 
# missile_aid_df <- missile_aid_df[,c(2,7)]

# # Summarizing by day, note there is no lag
# daily_aid_df <- aid_data %>%
#   filter(!is.na(date), !is.na(tot_activity_value_constant_currency)) %>%
#   mutate(day = floor_date(date, "day")) %>%
#   group_by(day) %>%
#   summarize(aid_daily_total = sum(tot_activity_value_constant_currency))

# Monthly aid sum 
monthly_aid_sum <- aid_data %>%
  filter(!is.na(date), !is.na(tot_activity_value_constant_currency)) %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month) %>%
  summarize(monthly_total_aid = sum(tot_activity_value_constant_currency)) %>%
  mutate(
    aid_m2m_change = monthly_total_aid - lag(monthly_total_aid),  #this lag is only to calculate the percent change
    percent_change_aid = (aid_m2m_change / lag(monthly_total_aid)) * 100)
monthly_aid_sum <- monthly_aid_sum[2:34,]

# Weekly aid sum 
weekly_aid_sum <- aid_data %>%
  filter(!is.na(date)) %>%
  mutate(tot_activity_value_constant_currency = replace_na(tot_activity_value_constant_currency, 0), 
         week = floor_date(date, "week")) %>%
  group_by(week) %>%
  summarize(weekly_aid_total = sum(tot_activity_value_constant_currency),
            patriot_aid = sum(Patriot.aid, na.rm = TRUE)) %>%
  mutate(
    aid_w2w_change = weekly_aid_total - lag(weekly_aid_total),  #this lag is only to calculate the percent change
    percent_change_aid = (aid_w2w_change / lag(weekly_aid_total)) * 100) %>%
  mutate(
    week_lag_percent_aid = lag(percent_change_aid),
    twoweek_lag_percent_aid = lag(percent_change_aid, 2)
  ) %>%
  complete(week = seq(min(week), max(week), by = "week"), fill = list(weekly_aid_total = 0))

weekly_aid_sum$percent_change_aid <- ifelse(is.na(weekly_aid_sum$percent_change_aid) | is.infinite(weekly_aid_sum$percent_change_aid), 0, weekly_aid_sum$percent_change_aid)
weekly_aid_sum$week_lag_percent_aid <- ifelse(is.na(weekly_aid_sum$week_lag_percent_aid) | is.infinite(weekly_aid_sum$week_lag_percent_aid), 0, weekly_aid_sum$week_lag_percent_aid)
weekly_aid_sum$twoweek_lag_percent_aid <- ifelse(is.na(weekly_aid_sum$twoweek_lag_percent_aid) | is.infinite(weekly_aid_sum$twoweek_lag_percent_aid), 0, weekly_aid_sum$twoweek_lag_percent_aid)


weekly_aid_sum <- weekly_aid_sum[5:145,]
```

```{r, echo = FALSE}
# Events data setup

events_data <- read.csv("/Users/briannapenkala/Downloads/Capstone/Working Events Data 4_6.csv")

events_data <- events_data %>%
  mutate(event_date = as.Date(event_date, format = "%m/%d/%y")) %>%
  rename(date = event_date) %>%
  mutate(russian_missiles = as.numeric(russian_missiles),
         russian_drones = as.numeric(russian_drones))

# Setting up weather data
weather_data <- read.csv("/Users/briannapenkala/Downloads/Capstone/48.36007018, 36.64711407 2022-02-07 to 2024-10-31.csv")
weather_data <- rename(weather_data, date = datetime) %>%
  mutate(date = as.Date(date, format("%Y-%m-%d")))
weather_data <- weather_data[,c(2,11,18)]

# Joining weather data and events data
events_data <- left_join(events_data, weather_data, by = "date")

# # Summarizing by day
# daily_event_df <- events_data %>%
#   filter(!is.na(date)) %>%
#   mutate(day = floor_date(date, "day")) %>%
#   group_by(day) %>%
#   summarize(event_daily_total = n())

# Weekly event sum
weekly_event_sum <- events_data %>%
  filter(!is.na(date)) %>%
  mutate(week = floor_date(date, "week")) %>%
  group_by(week) %>%
  summarize(weekly_event_total = n(), 
            ukrainian_instigated_events = sum(AggressorCoded), 
            russian_missiles = sum(russian_missiles), 
            russian_drones = sum(russian_drones), 
            avg_precip = round(mean(precip), 3), 
            avg_windspeed = round(mean(windspeed), 3))

weekly_event_sum$russian_instigated_events <- weekly_event_sum$weekly_event_total - weekly_event_sum$ukrainian_instigated_events

weekly_event_sum <- weekly_event_sum[4:nrow(weekly_event_sum),]
weekly_event_sum <- weekly_event_sum %>% 
  mutate(
  w2w_change_total = weekly_event_total - lag(weekly_event_total),  #this lag is only to calculate the percent change
  percent_change_total = (w2w_change_total / lag(weekly_event_total)) * 100) %>%
  mutate(
  w2w_change_uk = ukrainian_instigated_events - lag(ukrainian_instigated_events),  #this lag is only to calculate the percent change
  percent_change_ukraine = (w2w_change_uk / lag(ukrainian_instigated_events)) * 100) %>%
  mutate(
  w2w_change_ru = russian_instigated_events - lag(russian_instigated_events),  #this lag is only to calculate the percent change
  percent_change_russia = (w2w_change_ru / lag(russian_instigated_events)) * 100)

# Dataset for missile regressions
missile_events <- events_data %>%
  filter(russian_missiles == 1)

# Dataset for drone regressions
drones_dataset <- events_data %>%
  filter(russian_drones == 1)
antidrone_aid_df <- data.frame(date = aid_data$date, antidrone_aid = aid_data$antidrone_aid)
drones_dataset <- full_join(drones_dataset[,c(1,13,14,24)], antidrone_aid_df, by = "date")
drones_dataset$antidrone_aid[is.na(drones_dataset$antidrone_aid)] <- 0
drones_dataset$week_lag_aid <- lag(drones_dataset$antidrone_aid, 2)

monthly_event_sum <- events_data %>%
  filter(!is.na(date)) %>%
  mutate(month = floor_date(date, "month")) %>%
  group_by(month) %>%
  summarize(monthly_total_events = n()) %>%
  mutate(
    events_m2m_change = monthly_total_events - lag(monthly_total_events),  #this lag is only to calculate the percent change
    events_percent_change = (events_m2m_change / lag(monthly_total_events)) * 100)
```

```{r, echo = FALSE, message = FALSE}
# Merging data by given dates, no lag, no percent change (FOR STAGE 2)
# byday_data <- full_join(daily_aid_df, daily_event_df, by = "day")
# byday_data
# byday_data$aid_daily_total <- ifelse(is.na(byday_data$aid_daily_total), 0, byday_data$aid_daily_total)

# By week data
byweek_data <- full_join(weekly_aid_sum, weekly_event_sum, by = "week")
# Adding search data to week data
search_data <- read_csv("/Users/briannapenkala/Downloads/Capstone/SearchData.csv")
search_data$Week <- as.Date(search_data$Week, format = "%m/%d/%y")
search_data <- search_data[,c(1,9)] # for the sake of matching aid data
search_data <- search_data[6:146,]
search_data <- search_data %>%
  rename(week = Week)
byweek_data <- full_join(byweek_data, search_data, by = "week")
byweek_data <- as.data.frame(byweek_data) %>%
  mutate(across(everything(), ~replace_na(., 0)))

byweek_data <- byweek_data %>%
  mutate(aidgiven = if_else(weekly_aid_total == 0, 0, 1),
    abspercentukraine = abs(percent_change_ukraine), 
    absaidpercentchange = abs(percent_change_aid)) %>%
  mutate(aidgiven_week_lag = lag(aidgiven)) %>%
  mutate(aidgiven_twoweek_lag = lag(aidgiven, 2))
byweek_data$aidgiven_week_lag <- ifelse(is.na(byweek_data$aidgiven_week_lag), 0, byweek_data$aidgiven_week_lag)
byweek_data$aidgiven_twoweek_lag <- ifelse(is.na(byweek_data$aidgiven_twoweek_lag), 0, byweek_data$aidgiven_twoweek_lag)
```

## Top/bottom analysis

```{r, echo = FALSE}
top25_aid <- byweek_data %>%
  arrange(desc(percent_change_aid)) %>%
  slice_head(n = 25) %>%
  dplyr::select(week, percent_change_aid)

bottom25_aid <- byweek_data %>%
  arrange(percent_change_aid) %>%
  slice_head(n = 25) %>%
  dplyr::select(week, percent_change_aid)

top25_ukevents <- byweek_data %>%
  arrange(desc(percent_change_ukraine)) %>%
  slice_head(n = 25) %>%
  dplyr::select(week, percent_change_ukraine)

bottom25_ukevents <- byweek_data %>%
  arrange(percent_change_ukraine) %>%
  slice_head(n = 25) %>%
  dplyr::select(week, percent_change_ukraine)

top25 <- full_join(top25_aid, top25_ukevents, by = "week") %>%
  mutate(classification = "top")
bottom25 <- full_join(bottom25_aid, bottom25_ukevents, by = "week") %>%
  mutate(classification = "bottom")
all25 <- full_join(top25, bottom25, by = "week") %>%
  mutate(percent_change_aid = coalesce(percent_change_aid.x, percent_change_aid.y)) %>%
  mutate(percent_change_ukraine = coalesce(percent_change_ukraine.x, percent_change_ukraine.y))
all25 <- all25[,c(1, 8, 9)] 
all25 <- all25 %>%
    mutate(classification_ukraine = case_when(
    percent_change_ukraine <= -18.96552 ~ "low", 
    percent_change_ukraine >= 23.18841 ~ "high")) %>%
    mutate(classification_aid = case_when(
      percent_change_aid <= -90.58176 ~ "low",
      percent_change_aid >= 810 ~ "high")) %>%
    mutate(aidukraine_classification = paste(classification_aid,classification_ukraine)) %>%
  mutate(abs_aid = abs(percent_change_aid)) %>%
  mutate(abs_ukraine = abs(percent_change_ukraine)) 

both25 <- all25 %>%
  drop_na(percent_change_aid, percent_change_ukraine) %>%
  mutate(abs_aid = abs(percent_change_aid)) %>%
  mutate(abs_ukraine = abs(percent_change_ukraine)) %>%
  mutate(aidukraine_classification = paste(classification_aid,classification_ukraine))
both25 <- both25[,-c(4, 5)]


# aid_uk_all25 <- ggplot(data = all25, aes(x = week)) +
#   geom_point(aes(y = percent_change_aid, color = "Scaled Percent Change Aid")) + 
#   scale_color_manual(values = c("Scaled Percent Change Aid" = "blue",
#                                "Percent Change Ukraine" = "green")) +  
#   labs(title = "Aid Percent Change vs. Ukraine Percent Change (Top/bottom 25 with data for both)",
#        x = "Week", y = "Percent Change") +
#   theme_minimal() +
#   theme(legend.title = element_blank())
# aid_uk_all25

```

Top/bottom 25 aid and events percent changes (only rows with data in both columns)

```{r, echo = FALSE, warning = FALSE}
ggplot(aes(percent_change_ukraine, percent_change_aid/200), data = both25) +
  geom_point(aes(color = aidukraine_classification), alpha = 0.6) +
  ylim(-3, 20) +
  labs(title = "Relationship Between Aid and Events",
       x = "Percent Change in Ukraine Events",
       y = "Percent Change in Aid", 
       color = "Classification (aid first)") +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"), 
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))
```

```{r, echo = FALSE}
# Line of best fit example
ggplot(aes(abs_ukraine, abs_ukraine/100), data = both25) +
  geom_point(aes(color = aidukraine_classification), alpha = 0.6) +
  ylim(-3, 5) +
  labs(title = "Relationship Between Aid and Events",
       x = " Absolute Value of Percent Change in Ukraine Events",
       y = " Absolute Value of Percent Change in Aid", 
       color = "Classification (aid first)") +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"), 
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))
```

## Summary stats

Summary Statistics

```{r, results = 'asis', echo = FALSE}
labeled_data <- byweek_data[,c("week", "weekly_aid_total", "percent_change_aid", "weekly_event_total", "russian_missiles", "russian_drones", "percent_change_total", "percent_change_ukraine", "percent_change_russia", "search_score")]

names(labeled_data) <- c("Week","Weekly aid total (euro)", "Change in aid (%)", "Weekly event total", "Russian missile use", "Russian drone use", "Change in total events (%)", "Change in Ukrainian events (%)", "Change in Russian events (%)", "Search score")
summ_stats <- stargazer(labeled_data, type = "latex", summary = TRUE, font.size = "scriptsize", title = "Summary Statistics", digits = 2)
```

## Correlation matrix

```{r, echo = FALSE}
# Creating correlation matrix (extra parameter to deal with NAs)
corr_matrix <- cor(labeled_data[,c(2, 7, 8, 9)], use = "complete.obs")

par(family = "Times New Roman")
# Correlation plot (https://www.sthda.com/english/wiki/visualize-correlation-matrix-using-correlogram)
corrplot <- corrplot(corr_matrix, type = "upper", method = "color", order = "hclust", tl.col = "black", tl.srt = 45, tl.cex = .9, addCoef.col = "darkgrey", outline = TRUE)
# (type is layout, hclust is heirarchical ordering)

corr_test <- cor(byweek_data[,c(5,12,13,18,20,21)], use = "complete.obs")
corrplot_test <- corrplot(corr_test,  method = "color", order = "hclust", tl.col = "black", tl.srt = 45, tl.cex = .9, addCoef.col = "darkgrey", outline = TRUE)
```

## Visualizations

```{r, echo = FALSE}

## Data visualization

interest_aid_viz <- ggplot(aes(x = week), data = byweek_data) + 
  geom_line(aes(y = rescale(weekly_aid_total), color = "Aid"), linewidth = 1) + 
  geom_line(aes(y = rescale(search_score), color = "Search score"), linewidth = 1) +
  scale_color_manual(values = c("Search score" = "cadetblue4", "Aid" = "lightsalmon2")) +
  scale_y_continuous(
    name = "Standardized Value",
    sec.axis = sec_axis(~ . , name = "Standardized Value") 
  ) +
  labs(title = "Search Score and Aid by Week", 
       color = "Legend", 
       x = "Week") + 
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"), 
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))
interest_aid_viz
```

```{r, echo = FALSE}
# events_aid_viz <- ggplot(aes(x = week), data = byweek_data) + 
#   geom_line(aes(y = percent_change_aid, color = "Aid"), linewidth = 1) + 
#   #geom_line(aes(y = rescale(percent_change_ukraine), color = "Ukraine"), linewidth = 1) +
#   scale_color_manual(values = c("Ukraine" = "cadetblue4", "Aid" = "lightsalmon2")) +
# 
#   labs(title = "Ukraine by Week", 
#        color = "Legend", 
#        x = "Week") + 
#   theme_minimal(base_family = "Times New Roman") +
#   theme(
#     text = element_text(family = "Times New Roman"),
#     axis.title = element_text(family = "Times New Roman"), 
#     axis.text = element_text(family = "Times New Roman"),
#     plot.title = element_text(family = "Times New Roman"))
# events_aid_viz
```

```{r, echo = FALSE}
# monthly_combined <- monthly_aid_sum %>%
#   rename(Aid = percent_change_aid) %>%
#   full_join(monthly_event_sum %>% rename(Event = events_percent_change), by = "month") %>%
#   pivot_longer(cols = c(Aid, Event), names_to = "Type", values_to = "Percent_Change") 
# 
# # Create the bar plot with side-by-side bars
# events_aid_viz <- ggplot(monthly_combined, aes(y = (Percent_Change), fill = Type)) +
#   geom_histogram(position = "dodge") +
#   scale_fill_manual(values = c("Aid" = "cadetblue4", "Event" = "lightsalmon2")) +
#   scale_y_continuous(
#     name = "Percent Change (%)"
#   ) +
#   labs(title = "Events and Aid Percent Change by Month",
#        fill = "Legend",
#        x = "Month") +
#   theme_minimal() +
#   theme_minimal(base_family = "Times New Roman") +
#   theme(
#     text = element_text(family = "Times New Roman"),
#     axis.title = element_text(family = "Times New Roman"), 
#     axis.text = element_text(family = "Times New Roman"),
#     plot.title = element_text(family = "Times New Roman"))
# 
# 
# events_aid_viz
```

```{r, echo = FALSE}
# interest_events_viz <- ggplot(aes(x = week), data = byweek_data) + 
#   geom_line(aes(y = rescale(search_score), color = "Search score")) +
#   geom_line(aes(y = rescale(weekly_event_total), color = "Event")) + 
#   scale_color_manual(values = c("Search score" = "cadetblue4", "Event" = "lightsalmon2")) +
#   scale_y_continuous(
#     name = "Standardized Value",
#     sec.axis = sec_axis(~ . , name = "Standardized Value") 
#   ) +
#   labs(title = "Search Score and Events by Week", 
#        color = "Legend", 
#        x = "Week")
# interest_events_viz
```

```{r, echo = FALSE}
# Aid and Ukrainian instigated

monthly_combined <- left_join(monthly_aid_sum, monthly_event_sum, by = "month")
monthly_combined <- monthly_combined %>%
  mutate(
    aid_percent_scaled = (percent_change_aid - min(percent_change_aid, na.rm = TRUE)) / 
                         (max(percent_change_aid, na.rm = TRUE) - min(percent_change_aid, na.rm = TRUE)),
    events_percent_scaled = (events_percent_change - min(events_percent_change, na.rm = TRUE)) / 
                            (max(events_percent_change, na.rm = TRUE) - min(events_percent_change, na.rm = TRUE))
  )

monthly_long_scaled <- monthly_combined %>%
  select(month, aid_percent_scaled, events_percent_scaled) %>%
  pivot_longer(cols = c(aid_percent_scaled, events_percent_scaled),
               names_to = "Type", 
               values_to = "Scaled_Change")

# ---- Plot the Normalized Side-by-Side Bar Chart ----
aid_ukinst <- ggplot(monthly_long_scaled, aes(x = month, y = Scaled_Change, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_minimal() +
  labs(title = "Normalized Percent Change: Aid vs Events",
       x = "Month",
       y = "Scaled Change (0-1)",
       fill = "Category") +
  scale_fill_manual(values = c("aid_percent_scaled" = "cadetblue4", "events_percent_scaled" = "lightsalmon2"), labels = c("aid_percent_scaled" = "Change in aid (%)", 
               "events_percent_scaled" = "Change in events (%)")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"), 
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))

aid_ukinst
```

```{r, echo = FALSE, include = FALSE}
# Aid by country 

start_date <- as.Date("2022-02-20")
end_date <- as.Date("2024-10-31")

aid_data_graph <- aid_data %>%
  filter(date >= start_date & date <= end_date) %>%
  group_by(donor) %>%
  summarize(total_aid = sum(tot_activity_value_constant_currency, na.rm = TRUE)) %>%
  arrange(desc(total_aid))
aid_data_graph <- aid_data_graph[1:10,]
  
aid_country <- ggplot(aes(x = reorder(donor, -total_aid), y = total_aid), data = aid_data_graph) +
  geom_bar(stat = "identity", fill = "cadetblue4") +
  theme_minimal() +
  labs(title = "Top Ten Aid Providers (02/20/2022- 10/31/2024)",
       x = "Donor",
       y = "Total Aid Provided (in 2021 euros)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +  # Rotate x-axis labels for readability
  scale_fill_viridis_d() + 
  scale_y_continuous(labels = comma) + 
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"), 
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"), 
    axis.text.x = element_text(angle = 45, hjust = 1))
  
aid_country
```

```{r, echo = FALSE, message = FALSE}
# Ukrainian events on Russian events
ukr_rus_events <- ggplot(byweek_data) + 
  geom_smooth(aes(x = week, y = percent_change_ukraine, color = "Change in Ukrainian events"), method = "loess", span = .09, se = FALSE) + 
  geom_smooth(aes(x = week, y = percent_change_russia, color = "Change in Russian events"), method = "loess", span = .09, se = FALSE) + 
  scale_color_manual(values = c("Change in Ukrainian events" = "blue", "Change in Russian events" = "red")) +
  labs(title = "Russian and Ukrainian Instigated Events Over Time", 
       x = "Week", 
       y = "Percent Change in Events", 
       color = "Legend") +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"),
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))

ukr_rus_events
```

```{r}
# Map of missile attacks

ukraine <- st_read("/Users/briannapenkala/Downloads/Capstone/gadm41_UKR_shp")
missiles_sf <- st_as_sf(missile_events, coords = c("longitude", "latitude"), crs = 4326)

missile_before1 <- missiles_sf %>% filter(date < as.Date("2022-12-21"))
missile_after1 <- missiles_sf %>% filter(date >= as.Date("2022-12-21") & date < as.Date("2023-06-01"))

missile_map_before1 <- ggplot() + 
  geom_sf(data = ukraine, fill = "white", color = "black") + 
  geom_sf(data = missile_before1 , color = "blue", alpha = 0.2) +
  ggtitle("Before Patriot Deployment") +
  theme(plot.title = element_text(size = 9)) + 
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"),
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))

missile_map_after1 <- ggplot() + 
  geom_sf(data = ukraine, fill = "white", color = "black") + 
  geom_sf(data = missile_after1 , color = "blue", alpha = 0.2) +
  ggtitle("After Patriot Deployment") +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"),
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))
        
(missile_map_before1 + missile_map_after1) +
   plot_annotation(
    title = "Missile Attacks in Ukraine Before and After Patriot Deployment", 
    theme = theme(plot.title = element_text(family = "Times New Roman")))
    #caption = "Before = 02/22/2022 - 12/21/2022. After = 12/21/2022 - 06/21/2023"
```

## T-tests

```{r, echo = FALSE}
## T-tests
ru_uk_ttest <- t.test(byweek_data$ukrainian_instigated_events, byweek_data$russian_instigated_events)

# First t-test
ru_uk_table <- hux(
  "T-statistic" = -28.345,
  "Degrees of Freedom" = 218.26, 
  "P-value" = "< 2.2e-16", 
  "95% Confidence Interval" = "-294.746 - (-221.623)"
)


# Table details
bold(ru_uk_table)[1,] <- TRUE
bottom_border(ru_uk_table)[0:1,] <- .4
align(ru_uk_table) <- "center"
stripe_rows(ru_uk_table, stripe1 = "white", stripe2 = "grey90")
set_caption(ru_uk_table, "Comparison of Mean Ukrainian and Russian-Instigated Events")
```

```{r, echo = FALSE}
# Ukraine events high aid low aid

high_aid <- byweek_data[111:115,]
low_aid <- byweek_data[128:132,]

low_high_ttest <- t.test(high_aid$percent_change_ukraine, low_aid$percent_change_ukraine, paired = TRUE)

low_high_ttest <- hux(
  "T-statistic" = -0.351,
  "Degrees of Freedom" = 4, 
  "P-value" = .7433, 
  "95% Confidence Interval" = "-45.597 - 35.363"
)


# Table details
bold(low_high_ttest)[1,] <- TRUE
bottom_border(low_high_ttest)[0:1,] <- .4
align(low_high_ttest) <- "center"
stripe_rows(low_high_ttest, stripe1 = "white", stripe2 = "grey90")
set_caption(low_high_ttest, "Comparison of Mean Ukrainian Event Percent Changes in High and Low Aid Periods")
```

# Regressions on Ukraine

```{r, echo = FALSE}

# Regressions no lag
basic_reg <- lm(percent_change_ukraine ~ percent_change_aid + percent_change_russia + avg_precip + avg_windspeed, data = byweek_data)

# Regressions one week lag
basic_reg_lag1 <- lm(percent_change_ukraine ~ week_lag_percent_aid + percent_change_russia + avg_precip + avg_windspeed, data = byweek_data)

# Regressions two week lag
basic_reg_lag2 <- lm(percent_change_ukraine ~ twoweek_lag_percent_aid + percent_change_russia + avg_precip + avg_windspeed, data = byweek_data)

# Instrument
inst_basic <- ivreg(formula = percent_change_ukraine ~ percent_change_aid + percent_change_russia + avg_precip + avg_windspeed | search_score, data = byweek_data)
summary(inst_basic)

output <- huxreg(basic_reg, 
                basic_reg_lag1, 
                basic_reg_lag2, 
                inst_basic,
                 coefs = c("Aid" = "percent_change_aid", 
                           "Russian-instigated events change (%)" = "percent_change_russia",
                           "Aid lagged one week" = "week_lag_percent_aid", 
                           "Aid lagged two weeks" = "twoweek_lag_percent_aid", 
                           "Average precipitation" = "avg_precip", 
                           "Average wind speed" = "avg_windspeed")) %>%
  set_caption("Percent Change Aid") %>%
  set_markdown_contents(1, 2, "OLS") %>%
  set_markdown_contents(1, 3, "OLS") %>%
  set_markdown_contents(1, 4, "OLS") %>%
  set_markdown_contents(1, 5, "2SLS") 
output
```



Where UVE shows Ukrainian-instigated events; RVE shows Russian-instigated events

```{r, echo = FALSE}
# Dummy variable regressions

# Regressions dummy no lag
basic_dummy <- lm(percent_change_ukraine ~ aidgiven + percent_change_russia + avg_precip + avg_windspeed, data = byweek_data)

# Regressions one week lag
basic_dummy_lag1 <- lm(percent_change_ukraine ~ aidgiven_week_lag + percent_change_russia + avg_precip + avg_windspeed, data = byweek_data)

# Regressions two week lag
basic_dummy_lag2 <- lm(percent_change_ukraine ~ aidgiven_twoweek_lag + percent_change_russia + avg_precip + avg_windspeed, data = byweek_data)

# Instrument
first_stage_aid_dummy <- lm(aidgiven ~ search_score, data = byweek_data)
fitted_aid_dummy <- fitted(first_stage_aid_dummy)
second_stage_aid_dummy <- lm(percent_change_ukraine ~ fitted_aid_dummy + percent_change_russia  + avg_precip + avg_windspeed, data = byweek_data)

# Week lag
first_stage_aid_dummy_lag <- lm(aidgiven_week_lag ~ search_score, data = byweek_data)
fitted_aid_dummy_lag <- fitted(first_stage_aid_dummy_lag)
second_stage_aid_dummy_lag <- lm(percent_change_ukraine ~ fitted_aid_dummy_lag + percent_change_russia  + avg_precip + avg_windspeed, data = byweek_data)

first_stage_aid_dummy_lag2 <- lm(aidgiven_twoweek_lag ~ search_score, data = byweek_data)
fitted_aid_dummy_lag2 <- fitted(first_stage_aid_dummy_lag2)
second_stage_aid_dummy_lag2 <- lm(percent_change_ukraine ~ fitted_aid_dummy_lag2 + percent_change_russia  + avg_precip + avg_windspeed, data = byweek_data)
#inst_basic_dummy <- ivreg(formula = percent_change_ukraine ~ aidgiven + percent_change_russia  + avg_precip + avg_windspeed | search_score, data = byweek_data)

output_dummy <- huxreg(basic_dummy,
                       basic_dummy_lag1, 
                       basic_dummy_lag2, 
                       second_stage_aid_dummy,
                       second_stage_aid_dummy_lag, 
                       second_stage_aid_dummy_lag2,
                 coefs = c("Aid" = "aidgiven",
                           "Aid" = "fitted_aid_dummy", 
                           "Aid lagged one week" = "aidgiven_week_lag", 
                           "Aid lagged one week" = "fitted_aid_dummy_lag", 
                           "Aid lagged two weeks" = "fitted_aid_dummy_lag2",
                           "Aid lagged two weeks" = "aidgiven_twoweek_lag",
                           "Russian-instigated events change (%)" = "percent_change_russia",
                           "Average precipitation" = "avg_precip", 
                           "Average wind speed" = "avg_windspeed")) %>%
  set_caption("Aid as a Dummy Variable") %>%
  set_markdown_contents(1, 2, "OLS") %>%
  set_markdown_contents(1, 3, "OLS") %>%
  set_markdown_contents(1, 4, "OLS") %>%
  set_markdown_contents(1, 5, "2SLS") 
output_dummy
```

First stage:
$$ {AidGiven_W} = \beta_0 + \beta_1\text{SearchScore}_W + u_W $$

Second stage:
$$ {UVE_W} = \beta_0 + \beta_1 \text{MilitaryAid}_{W-lag} + \beta_2 \text{RVE}_W + \beta_3 \text{AveragePrecipitation}_W + \beta_4 \text{AverageWindSpeed}_W + u_W $$

# Regressions on Russia

```{r}
# Russia regressions no lag
basic_reg_russia <- lm(percent_change_russia ~ percent_change_aid + percent_change_ukraine, data = byweek_data)

# Regressions one week lag
basic_reg_lag1_russia <- lm(percent_change_russia ~ week_lag_percent_aid + percent_change_ukraine, data = byweek_data)

# Regressions two week lag
basic_reg_lag2_russia <- lm(percent_change_russia ~ twoweek_lag_percent_aid + percent_change_ukraine, data = byweek_data)

# Instrument
inst_basic_russia <- ivreg(formula = percent_change_russia ~ percent_change_aid + percent_change_ukraine | search_score + percent_change_ukraine, data = byweek_data)

output_russia <- huxreg(basic_reg_russia, 
                basic_reg_lag1_russia, 
                basic_reg_lag2_russia, 
                inst_basic_russia,
                 coefs = c("Aid" = "percent_change_aid", 
                           "Ukrainian-instigated events change (%)" = "percent_change_ukraine",
                           "Aid lagged one week" = "week_lag_percent_aid", 
                           "Aid lagged two weeks" = "twoweek_lag_percent_aid")) %>%
  set_caption("Percent Change Aid Russia") %>%
  set_markdown_contents(1, 2, "OLS") %>%
  set_markdown_contents(1, 3, "OLS") %>%
  set_markdown_contents(1, 4, "OLS") %>%
  set_markdown_contents(1, 5, "2SLS") 
output_russia
```

```{r}
# Russia dummy variable regressions

# Regressions dummy no lag
basic_dummy_russia <- lm(percent_change_russia ~ aidgiven + percent_change_ukraine, data = byweek_data)

# Regressions one week lag
basic_dummy_lag1_russia <- lm(percent_change_russia ~ aidgiven_week_lag + percent_change_ukraine, data = byweek_data)

# Regressions two week lag
basic_dummy_lag2_russia <- lm(percent_change_russia ~ aidgiven_twoweek_lag + percent_change_ukraine, data = byweek_data)

# Instrument
inst_dummy_russia <- ivreg(formula = percent_change_russia ~ aidgiven + percent_change_ukraine | search_score + percent_change_ukraine, data = byweek_data)

output_dummy_russia <- huxreg(basic_dummy_russia,
                       basic_dummy_lag1_russia, 
                       basic_dummy_lag2_russia, 
                       inst_dummy_russia,
                 coefs = c("Aid" = "aidgiven", 
                           "Ukrainian-instigated events change (%)" = "percent_change_ukraine",
                           "Aid lagged one week" = "aidgiven_week_lag", 
                           "Aid lagged two weeks" = "aidgiven_twoweek_lag")) %>%
  set_caption("Aid as a Dummy Variable Russia") %>%
  set_markdown_contents(1, 2, "OLS") %>%
  set_markdown_contents(1, 3, "OLS") %>%
  set_markdown_contents(1, 4, "OLS") %>%
  set_markdown_contents(1, 5, "2SLS") 
output_dummy_russia
```

# Regressions on missiles

```{r}
# Missiles regressions

# Patriot aid on missile use (expect to decrease)
missile_reg <- lm(russian_missiles ~ patriot_aid, data = byweek_data)

missile_reg_controlled <- lm(russian_missiles ~ patriot_aid + russian_drones, data = byweek_data)

missile_reg_inst <- ivreg(russian_missiles ~ patriot_aid + russian_drones | search_score + russian_drones, data = byweek_data)

output_missile <- huxreg(missile_reg, 
                missile_reg_controlled, 
                coefs = c("Patriot aid" = "patriot_aid", 
                           "Russian drones" = "russian_drones")) %>%
  set_caption("Russian Missile Use on Patriot Aid") %>%
  set_markdown_contents(1, 2, "OLS") %>%
  set_markdown_contents(1, 3, "OLS") 
output_missile
```

$$ {RussianMissileUse_W} = \beta_0 + \beta_1 \text{PatriotAid}_W + \beta_2 \text{RussianDroneUse}_W + u_W $$
```{r}
# Patriot aid on drone use (expect to increase)
missile_reg_drone <- lm(russian_drones ~ patriot_aid, data = byweek_data)
summary(missile_reg_drone)

ex <- lm(russian_missiles ~ russian_drones, data = byweek_data)
summary(ex)

# Drone regressions (russian drone activity on anti drone aid)
antidrone_reg <- lm(russian_drones ~ week_lag_aid, data = drones_dataset)
summary(antidrone_reg)
```


```{r, echo = FALSE}
# Graph comparing the amount of aid and events percentage ranges 
# 
# ggplot(aes(x = aidgiven), data = byweek_data) + 
#   geom_col(aes(y = percent_change_ukraine))
```

```{r}
ggplot(aes(x = week), data = byweek_data) +
  geom_smooth(aes(y = rescale(russian_missiles), color = "Russian missile use")) + 
  geom_smooth(aes(y = rescale(russian_drones), color = "Russian drone use")) + 
  geom_smooth(aes(y = rescale(patriot_aid), color = "Patriot aid provided")) + 
  scale_color_manual(values = c("Russian missile use" = "blue", "Russian drone use" = "orange", "Patriot aid provided" = "red")) +
  labs(title = "Russian Missile and Drone Use Compared with Patriot Aid", 
       x = "Week", 
       y = "Rescaled Amounts", 
       color = "Legend") + 
  theme_minimal(base_family = "Times New Roman") +
  theme(
    text = element_text(family = "Times New Roman"),
    axis.title = element_text(family = "Times New Roman"), 
    axis.text = element_text(family = "Times New Roman"),
    plot.title = element_text(family = "Times New Roman"))
  
```
